Optimizing Automated Finite Element Integration through Expression Rewriting and Code Specialization

### 2014-08-05 TOMS_Paper/assembly.tex
Now use newer pictures

\begin{figure}[t]
\centering     
\subfigure{\includegraphics[scale=0.17]{perf-results/helmholtz/FiredrakeFormsCoffee_bar_q1_p1_formhelmholtz_speedup}}
\subfigure{\includegraphics[scale=0.17]{perf-results/helmholtz/FiredrakeFormsCoffee_bar_q1_p2_formhelmholtz_speedup}}
\subfigure{\includegraphics[scale=0.17]{perf-results/helmholtz/FiredrakeFormsCoffee_bar_q1_p3_formhelmholtz_speedup}}
\subfigure{\includegraphics[scale=0.17]{perf-results/helmholtz/FiredrakeFormsCoffee_bar_q1_p4_formhelmholtz_speedup}}
\subfigure{\includegraphics[scale=0.17]{perf-results/helmholtz/FiredrakeFormsCoffee_bar_q2_p1_formhelmholtz_speedup}}
\subfigure{\includegraphics[scale=0.17]{perf-results/helmholtz/FiredrakeFormsCoffee_bar_q2_p2_formhelmholtz_speedup}}
\subfigure{\includegraphics[scale=0.17]{perf-results/helmholtz/FiredrakeFormsCoffee_bar_q2_p3_formhelmholtz_speedup}}
\subfigure{\includegraphics[scale=0.17]{perf-results/helmholtz/FiredrakeFormsCoffee_bar_q2_p4_formhelmholtz_speedup}}
\subfigure{\includegraphics[scale=0.17]{perf-results/helmholtz/FiredrakeFormsCoffee_bar_q3_p1_formhelmholtz_speedup}}
\subfigure{\includegraphics[scale=0.17]{perf-results/helmholtz/FiredrakeFormsCoffee_bar_q3_p2_formhelmholtz_speedup}}
\subfigure{\includegraphics[scale=0.17]{perf-results/helmholtz/FiredrakeFormsCoffee_bar_q3_p3_formhelmholtz_speedup}}
\subfigure{\includegraphics[scale=0.17]{perf-results/helmholtz/FiredrakeFormsCoffee_bar_q3_p4_formhelmholtz_speedup}}
\subfigure{\includegraphics[scale=0.17]{perf-results/helmholtz/FiredrakeFormsCoffee_bar_q4_p1_formhelmholtz_speedup}}
\subfigure{\includegraphics[scale=0.17]{perf-results/helmholtz/FiredrakeFormsCoffee_bar_q4_p2_formhelmholtz_speedup}}
\subfigure{\includegraphics[scale=0.17]{perf-results/helmholtz/FiredrakeFormsCoffee_bar_q4_p3_formhelmholtz_speedup}}
\subfigure{\includegraphics[scale=0.17]{perf-results/helmholtz/FiredrakeFormsCoffee_bar_q4_p4_formhelmholtz_speedup}}
\caption{Helmholtz results.}\label{fig:helmholtz}
\end{figure}

@@

\begin{figure}[t]
\centering     
\subfigure{\includegraphics[scale=0.17]{perf-results/elasticity/FiredrakeFormsCoffee_bar_q1_p1_formelasticity_speedup}}
\subfigure{\includegraphics[scale=0.17]{perf-results/elasticity/FiredrakeFormsCoffee_bar_q1_p2_formelasticity_speedup}}
\subfigure{\includegraphics[scale=0.17]{perf-results/elasticity/FiredrakeFormsCoffee_bar_q1_p3_formelasticity_speedup}}
\subfigure{\includegraphics[scale=0.17]{perf-results/elasticity/FiredrakeFormsCoffee_bar_q1_p4_formelasticity_speedup}}
\subfigure{\includegraphics[scale=0.17]{perf-results/elasticity/FiredrakeFormsCoffee_bar_q2_p1_formelasticity_speedup}}
\subfigure{\includegraphics[scale=0.17]{perf-results/elasticity/FiredrakeFormsCoffee_bar_q2_p2_formelasticity_speedup}}
\subfigure{\includegraphics[scale=0.17]{perf-results/elasticity/FiredrakeFormsCoffee_bar_q2_p3_formelasticity_speedup}}
\subfigure{\includegraphics[scale=0.17]{perf-results/elasticity/FiredrakeFormsCoffee_bar_q2_p4_formelasticity_speedup}}
\subfigure{\includegraphics[scale=0.17]{perf-results/elasticity/FiredrakeFormsCoffee_bar_q3_p1_formelasticity_speedup}}
\subfigure{\includegraphics[scale=0.17]{perf-results/elasticity/FiredrakeFormsCoffee_bar_q3_p2_formelasticity_speedup}}
\subfigure{\includegraphics[scale=0.17]{perf-results/elasticity/FiredrakeFormsCoffee_bar_q3_p3_formelasticity_speedup}}
\subfigure{\includegraphics[scale=0.17]{perf-results/elasticity/FiredrakeFormsCoffee_bar_q3_p4_formelasticity_speedup}}
\subfigure{\includegraphics[scale=0.17]{perf-results/elasticity/FiredrakeFormsCoffee_bar_q4_p1_formelasticity_speedup}}
\subfigure{\includegraphics[scale=0.17]{perf-results/elasticity/FiredrakeFormsCoffee_bar_q4_p2_formelasticity_speedup}}
\subfigure{\includegraphics[scale=0.17]{perf-results/elasticity/FiredrakeFormsCoffee_bar_q4_p3_formelasticity_speedup}}
\subfigure{\includegraphics[scale=0.17]{perf-results/elasticity/FiredrakeFormsCoffee_bar_q4_p4_formelasticity_speedup}}
\caption{Elasticity results.}\label{fig:elasticity}
\end{figure}

% Mass DGEMM utile explicit method etc

>>>>

\begin{figure}[t]  
\includegraphics[scale=0.7]{perf-results/helmholtz}
\caption{Helmholtz results.}\label{fig:helmholtz}
\end{figure}

@@

\begin{figure}[t]  
\includegraphics[scale=0.7]{perf-results/elasticity}
\caption{Elasticity results.}\label{fig:elasticity}
\end{figure}
% Mass DGEMM utile explicit method etc
